Adopting agile in the large: motivations, success factors and challenges

### 2014-04-23 journal/article.tex
Reasons to change: external issues

@@

        &  \multicolumn{2}{l}{Something must be done to remain competitive} \\

@@

        &  \multicolumn{2}{l}{General problems with management of software development} \\
        &  &  General management dysfunction  \\
        &  &  Problems with motivation and morale  \\
        &  &  Problems coordinating a growing organization  \\

@@

The most prominent reason for introducing agile methods was the demand to
deliver software more frequently. A frequent statement was that it was necessary
to reduce the Time To Market (TTM) [P17, P18, P32, P39, P47]. As stated in one
study ``The market was moving faster than the development group was able to
deliver'' [P38].

* TTM, lead time

[P17]
Faster TTM
"BMC decided to introduce a new generation of their own successful products before competitors could."

[P17]
Product needs to be improved quickly.
The deadline is looming (TTM) "Target delivery of the first release was less than a year away"

[P18]
Reduce TTM "Ericsson set a corporate R\&D goal to reduce Time to Market"
Faster cycles became necessary "This forced the PDU to deliver products in much short cycles."

[P18]
Reduction in lead time, increase in responsiveness, "both appealing and necessary" "in our ‘new’ multimedia market place"

[P32]
TTM must be reduced
"BT is facing rapid marketplace changes that require it to radically increase its speed to market."

[P38]
TTM must be improved, to remain competitive
"The market was moving faster than the development group was able to deliver."

[P39]
The TTM needed to be shortened
The testing time needed to be shortened

[P47]
There was a desire to reduce TTM

* Long cycle time is seen as a problem in itself

[P2]
They THINK that agile will make them deliver faster

[P8]
There are challenges in achieving faster and more frequent delivery.

[P25]
Long cycle time is seen as a general problem

[P33]
Long cycles is seen as a problem in itself
"the number of releases had slowed to one major release per year"

[P36]
A "small system" needed to be put in place as fast as possible

[P41]
The goal was to "deliver better quality faster"

[P16]
Lack of feedback
"many people in R\&D had not participated in a major release"
Release cycles are too long, which is clearly problematic

[P49]
It takes ``too long to develop''
It takes ``too long to deploy''
Too little assurance that the result will be good in the changing marketplace
"software was taking too long to develop, too long to deploy, and providing too
little assurance that what was either developed or deployed was really going to
ferry the corporation through the tumultuous waters of its marketplace"

* Slowness combined with cost

[P36]
It is realized that development was slow, and needs to be improved
"Business ... felt the all-too-common frustrations with the pace and cost of development."

[P46]
Development is "too slow and too expensive across the board"

* Customers or ``business'' demand shorter cycles

[P23]
Speed of delivery
"Speed of delivery is of the essence – customers are no longer prepared to wait for 18 months or more for solutions to be delivered."

[P39]
Project stakeholders demand "as early releases as possible"

[P46]
Business cared only about speed to value.

[P5]
New solutions must be delivered on a fast schedule
"The engineering team had to deliver rapid incremental improvement."
Software quality needs to be improved.
"Business pressure for rapid improvement was growing."
"The organization would be required to demonstrate significant improvement in a very short timeframe. It was clear traditional software development methodologies simply would not work."

* Length delivery is a problem in the competition

[P11]
"we couldn't do business as usual" --> delivery speed must be increased, to remain competitive

[P19]
Fear of competitors, something must be done
Long release cycles/duration are "an alarming state that could enable competitors to gain market share"

* Faster is better ROI

[P8]
Provide within shorter cycles in order to focus on highest ROI

* Timeliness, accuracy

[P9]
Product deliveries must be timely, to remain competitive

[P15]
The number of releases needed to be increased, for accuracy

>>>>

        &  \multicolumn{2}{l}{Something must be done in order to remain competitive} \\

@@

@@

        &  \multicolumn{2}{l}{General problems with management of software development} \\
        &  &  Management dysfunction  \\
        &  &  Problems with motivation and morale  \\
        &  &  Problems coordinating a growing organization  \\

@@

The most prominent reason for introducing agile methods was the demand to
deliver software faster and more frequently. A common statement was that it was
necessary to reduce the Time To Market (TTM) [P17, P18, P32, P39, P47]. As
stated in one study: ``The market was moving faster than the development group
was able to deliver'' [P38]. Long cycle time, i.e. time from start of project to
delivery, was seen as a problem in itself in some studies [P25, P36]. Many
studies indicated that the organizations set as one of the transformation goals
to deliver software faster [P2, P8]. Other cases described that development was
generally considered as slow [P36, P46, P49].

Commercial competition and market situation was seen as a trigger for
transformation. Especially speed of delivery was seen as a means to respond to
the competition [P9, P38]. As Greening describes: ``The average release duration
peaked at 41 and 35 months, an alarming state that could enable competitors to
gain market share.'' [P19]. In many cases the transformation was seen as
essential for the company to remain competitive [P11, P18, P42, P49]. For
instance, British Telecom realized that ``From a strategic view, there is little
alternative than to change the old ways of working'' [P32].

Demands for change and improvement were also expressed by internal and external
customers. Again, the requests of the customers reflected the need of faster
development and release cycles [P5, P39]. As described in one study: ``Speed of
delivery is of the essence – customers are no longer prepared to wait for 18
months or more for solutions to be delivered'' [P23]. In some cases business
partners expressed mistrust in the original way of conducting development [P40,
P46].

% * Timeliness, accuracy
% 
% [P15]
% The number of releases needed to be increased, for accuracy
